---
title: "Project_582"
author: "Error_Loading"
date: "1/26/2021"
output: 
  html_document:
      toc: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
          
---

train_raw %>% group_by(y) %>% summarize(count=n()) 
1565 a
509 b

DMwR::SMOTE: k=5, perc.over = 200, perc.under=200
2036 a
1527 b
Aşağıdaki modeller bunu kullanıyor
smotefamily::SMOTE

PRA test 84, train 81 seed70
RF 90-98, subm0.841
RF2 90test-99train 0.84subm
DT 84-84
SGB 88 -100 no tune, 89-90 tune with gbmGrid_forever, 82 subm
82-81 "svmLinear" 
88-95 "svmRadial" subm76
NN 85-93, subm 81.2



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, conflict=FALSE, warning=FALSE, message=FALSE, error = FALSE, comment = FALSE)
```

# Introduction
Problem description, summary of the proposed approach, descriptive
analysis of the given data.

```{r submission_functions_dont_touch}
require(jsonlite)
require(httr)
require(data.table)

get_token <- function(username, password, url_site){
    
    post_body = list(username=username,password=password)
    post_url_string = paste0(url_site,'/token/')
    result = POST(post_url_string, body = post_body)

    # error handling (wrong credentials)
    if(result$status_code==400){
        print('Check your credentials')
        return(0)
    }
    else if (result$status_code==201){
        output = content(result)
        token = output$key
    }

    return(token)
}

send_submission <- function(predictions, token, url_site, submit_now=F){
    
    format_check=check_format(predictions)
    if(!format_check){
        return(FALSE)
    }
    
    post_string="list("
    for(i in 1:length(predictions)){
        if(i<length(predictions)){
            post_string=sprintf("%s%s,",post_string,predictions[i])
        } else {
            post_string=sprintf("%s%s)",post_string,predictions[i])
        }
    }
    
    submission = eval(parse(text=post_string))
    json_body = jsonlite::toJSON(submission, auto_unbox = TRUE)
    submission=list(submission=json_body)
    print(submission)

    if(!submit_now){
        print("You did not submit.")
        return(FALSE)      
    }
    

    header = add_headers(c(Authorization=paste('Token',token,sep=' ')))
    post_url_string = paste0(url_site,'/submission/')
    result = POST(post_url_string, header, body=submission)
    
    if (result$status_code==201){
        print("Successfully submitted. Below you can see the details of your submission")
    } else {
        print("Could not submit. Please check the error message below, contact the assistant if needed.")
    }
    
    print(content(result))
    
}

check_format <- function(predictions){
    
    if(all(is.numeric(predictions)) & all(predictions<=1)){
        print("Format OK")
        return(TRUE)
    } else {
        print("Wrong format")
        return(FALSE)
    }
    
}
```


```{r libraries}
#importing the libraries
library(caret)
library(dplyr)
library(corrplot)
library(data.table)
library(glmnet)
library(rpart)
library(TunePareto)
library(randomForest)
library(tidyverse)
library(ggplot2)
library(pROC)
library(ROSE)
library(nnet)
library(skimr)
```

```{r dataset_manip}
train_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTrain.csv?token=ANPOH4IJOQLOLAD4XZY5ODTAFOXIC")
test_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTest.csv?token=ANPOH4JMDTUCP6TB4RWTZSTAFOXFY")

#skim(train_raw)

#no NA values, good
#train_raw %>% summarise_all(~ sum(is.na(.))) 
#test_raw %>% summarise_all(~ sum(is.na(.))) 

#to see the imbalance
#train_raw %>% group_by(y) %>% summarize(count=n()) 
#ggplot(train_raw, aes(x=y )) + geom_bar(color="blue", fill=rgb(0.1,0.4,0.5,0.7) )

# train x50 ve x52 zero column, no variation, nothing to learn
# test x50 ve x52 zero değil ama öğrenmediğini predict edemez
# droplamak durumundayız
train <- train_raw %>% select(-x50, -x52, x57, x37)
X_test_submission <- test_raw %>% select(-x50, -x52, -x37, -x57, -y)

# make all colns double for smote
train_y <- mlr::createDummyFeatures(train$y, train$y,  method="reference")
trainx <- train %>% select(-y)
train <- cbind(as.data.table(trainx), as.data.table(train_y)) %>% rename(y=b)

set.seed(70)
smote <- smotefamily::SMOTE(X=train, target=train$y, K=1, dup_size = 2)

final_train_smote <- smote[["data"]] %>% select(-class)
#final_train_smote %>% group_by(y) %>% summarize(count=n()) 

final_train_smote$y[final_train_smote$y==1] <- "b"
final_train_smote$y[final_train_smote$y==0] <- "a"


# cts olanlar ayrılıp scale edip cbind edilecek - X_test_submission ve train için, diğerleri factor yapılacak
colns <- colnames(final_train_smote)
cts_features <- c("x1", "x5", "x6", "x7", "x8", "x9", "x10", "x11", "x14", "x27", "x30", "x32", "x36", "x42")
categorical_features <- c("x2", "x3", "x4", "x12", "x13", "x15", "x16", "x17", "x18", "x19", "x20", "x21", "x22", "x23", "x24", "x25", "x26", "x28", "x29", "x31", "x33", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x47", "x48", "x49", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60")
categorical_features_y <- c("x2", "x3", "x4", "x12", "x13", "x15", "x16", "x17", "x18", "x19", "x20", "x21", "x22", "x23", "x24", "x25", "x26", "x28", "x29", "x31", "x33", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x47", "x48", "x49", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60", "y")

# scaling
train_cts_scaled <- final_train_smote %>% select(-y) %>% select(cts_features) %>% scale() %>% as.data.frame()

X_test_cts_scaled <-X_test_submission %>% select(cts_features) %>% scale() %>% as.data.frame()

# factorization
train_categorical <- final_train_smote %>% select(categorical_features)
train_categorical <- lapply(train_categorical, factor)
X_test_submission_categorical <- X_test_submission %>% select(categorical_features)
X_test_submission_categorical <- lapply(X_test_submission_categorical, factor)

train_categorical <- final_train_smote %>% select(categorical_features)

X_test_submission_categorical <- X_test_submission %>% select(categorical_features)

# scaled and factored
trainn <- cbind(as.data.table(train_cts_scaled), as.data.table(train_categorical), as.data.table(final_train_smote$y)) %>% rename(y=V1)
#levels(trainn$y) <- c("a", "b")
trainn$y <- as.factor(trainn$y)
final_train <- trainn
X_test_submission <- cbind(as.data.table(X_test_cts_scaled), as.data.table(X_test_submission_categorical))


#Correlation check
#corrplot(cor(train_cts_scaled, method = c("pearson")))
#corrplot(cor(X_test_cts_scaled, method = c("pearson")))


trainn <- final_train %>% select(-x59, -x26, -x49, -x46, -x43, -x60, -x29, -x55, -x31, -x18)

set.seed(1)
train_inds <- createDataPartition(y = 1:nrow(trainn), p = 0.8, list = F)
test <- trainn[-train_inds, ]
train <- trainn[train_inds, ]

train <- train
X_train <- train %>% select(-y)
y_train <- train %>% select(y)
X_test <- test %>% select(-y)
y_test <- test %>% select(y)

```

```{r model}
## RF 90-98 
set.seed(50)
m<-c(8, 10, 12, 15)
#for balanced folds: stratified =TRUE
# ntree is J=500 given in hw
J<-500 
# the minimal number of observations per tree leaf is nodesize 5 given in hw
min_size_of_terminal_nodes<-5
n_folds<-10
fitControl<-trainControl(method = "repeatedcv", number = n_folds, repeats = 1, classProbs = TRUE, search="random", savePred=TRUE, summaryFunction = twoClassSummary)   
rf_grid<-expand.grid(mtry = m)

set.seed(50)
model_RF <- train(y ~ ., data = train, method = "rf", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid, metric = "ROC")

pred_RF <- predict(model_RF, newdata=X_test)

cm_RF_test <- confusionMatrix(factor(pred_RF), factor(test$y))
cm_RF_train <- confusionMatrix(factor(predict(model_RF, newdata=X_train)), factor(train$y))

balanced_accuracy_test <- cm_RF_test[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_train <- cm_RF_train[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_test)
print(balanced_accuracy_train)


######  submission
set.seed(50)
m<-c(8, 10, 12)
#for balanced folds: stratified =TRUE
# ntree is J=500 given in hw
J<-500 
# the minimal number of observations per tree leaf is nodesize 5 given in hw
min_size_of_terminal_nodes<-5
n_folds<-10
fitControl<-trainControl(method = "repeatedcv", number = n_folds, repeats = 1, classProbs = TRUE, search="random", savePred=TRUE, summaryFunction = twoClassSummary)   
rf_grid<-expand.grid(mtry = m)
model_RF <- train(y ~ ., data = trainn, method = "rf", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid, metric = "ROC")

cm_pra_train <- confusionMatrix(factor(predict(model_RF, newdata=trainn[,-47])), factor(trainn$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

pred_RF1 <- predict(model_RF, newdata=X_test_submission, type = 'prob')
pred_RF <- pred_RF1[,2] #Bunu submitliyoruz


a <- model_RF[["finalModel"]][["importance"]] %>% as.data.frame()
colnames(a)[1] = "Importance"
a <- a %>% arrange(desc(Importance))

```





```{r submit}
# this part is main code
subm_url = 'http://46.101.121.83'

u_name = "Error_Loading"
p_word = "UHAxWUfYKVZNQmgq"
submit_now = TRUE

username = u_name
password = p_word

token = get_token(username=u_name, password=p_word, url=subm_url)

predictions <- pred_RF

send_submission(predictions, token, url=subm_url, submit_now= submit_now)
```

# Related Literature
Summarize relevant literature if there is any
# Approach
Explain your approach to this problem.
# Results
Provide your results and discussion.
# Conclusions and Future Work
Summarize your findings and comments regarding your
approach. What are possible extensions to have a better approach?
# Code
The Github link for the codes is (HERE)[].





# PRA

# RF

