---
title: "Project_582"
author: "Error_Loading"
date: "1/26/2021"
output: 
  html_document:
      toc: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
          
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, conflict=FALSE, warning=FALSE, message=FALSE, error = FALSE, comment = FALSE)
```

# Introduction
Problem description, summary of the proposed approach, descriptive
analysis of the given data.

```{r submission_functions_dont_touch}
require(jsonlite)
require(httr)
require(data.table)

get_token <- function(username, password, url_site){
    
    post_body = list(username=username,password=password)
    post_url_string = paste0(url_site,'/token/')
    result = POST(post_url_string, body = post_body)

    # error handling (wrong credentials)
    if(result$status_code==400){
        print('Check your credentials')
        return(0)
    }
    else if (result$status_code==201){
        output = content(result)
        token = output$key
    }

    return(token)
}

send_submission <- function(predictions, token, url_site, submit_now=F){
    
    format_check=check_format(predictions)
    if(!format_check){
        return(FALSE)
    }
    
    post_string="list("
    for(i in 1:length(predictions)){
        if(i<length(predictions)){
            post_string=sprintf("%s%s,",post_string,predictions[i])
        } else {
            post_string=sprintf("%s%s)",post_string,predictions[i])
        }
    }
    
    submission = eval(parse(text=post_string))
    json_body = jsonlite::toJSON(submission, auto_unbox = TRUE)
    submission=list(submission=json_body)
    print(submission)

    if(!submit_now){
        print("You did not submit.")
        return(FALSE)      
    }
    

    header = add_headers(c(Authorization=paste('Token',token,sep=' ')))
    post_url_string = paste0(url_site,'/submission/')
    result = POST(post_url_string, header, body=submission)
    
    if (result$status_code==201){
        print("Successfully submitted. Below you can see the details of your submission")
    } else {
        print("Could not submit. Please check the error message below, contact the assistant if needed.")
    }
    
    print(content(result))
    
}

check_format <- function(predictions){
    
    if(all(is.numeric(predictions)) & all(predictions<=1)){
        print("Format OK")
        return(TRUE)
    } else {
        print("Wrong format")
        return(FALSE)
    }
    
}
```


```{r libraries}
#importing the libraries
library(caret)
library(dplyr)
library(corrplot)
library(data.table)
library(glmnet)
library(rpart)
library(TunePareto)
library(randomForest)
library(tidyverse)
library(ggplot2)
library(pROC)
library(ROSE)
library(nnet)
library(skimr)
```

```{r dataset_manip}
train_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTrain.csv?token=ARPECO5RVGUHXHQVPPYNA3DAF7PTU")
test_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTest.csv?token=ARPECO77ESBHNVKCT2Q2PKTAF7PTA")

train <- train_raw %>% select(-x50, -x52, -x57, -x37, -x19, -x26, -x49, -x29, -x1, -x47, -x33, -x11, -x7, -x2, -x10, -x4)
X_test_submission <- test_raw %>% select(-x50, -x52, -x57, -x37, -x19, -x26, -x49, -x29, -x1, -x47, -x33, -x11, -x7, -x2, -x10, -x4, -y)
set.seed(1)
up_train <- upSample(x = train[, -ncol(train)], y = as.factor(train$y))   

# cts olanlar ayrılıp scale edip cbind edilecek - X_test_submission ve train için, diğerleri factor yapılacak
cts_features <- c("x5", "x6", "x8", "x9", "x14", "x27", "x30", "x32", "x36", "x42")
categorical_features <- c( "x3", "x12", "x13", "x15", "x16", "x17", "x18", "x20", "x21", "x22", "x23", "x24", "x25", "x28", "x31", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x48", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60")
categorical_features_y <- c( "x3", "x12", "x13", "x15", "x16", "x17", "x18", "x20", "x21", "x22", "x23", "x24", "x25", "x28", "x31", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x48", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60", "y")

# scaling
train_cts_scaled <- up_train %>% select(cts_features) %>% scale() %>% as.data.frame()

X_test_cts_scaled <-X_test_submission %>% select(cts_features) %>% scale() %>% as.data.frame()

# factorization
train_categorical <- up_train %>% select(-Class) %>% select(categorical_features)
train_categorical <- lapply(train_categorical, factor)
X_test_submission_categorical <- X_test_submission %>% select(categorical_features)
X_test_submission_categorical <- lapply(X_test_submission_categorical, factor)

train_categorical <- up_train %>% select(categorical_features)

X_test_submission_categorical <- X_test_submission %>% select(categorical_features)

# scaled and factored
trainn <- cbind(as.data.table(train_cts_scaled), as.data.table(train_categorical), as.data.table(up_train$Class))
#levels(trainn$y) <- c("a", "b")
trainn$V1 <- as.factor(trainn$V1)
up_train <- trainn
X_test_submission <- cbind(as.data.table(X_test_cts_scaled), as.data.table(X_test_submission_categorical))


fitControl <- trainControl(method = "repeatedcv", number = 10, verboseIter = TRUE, classProbs = TRUE)
tunegrid <- expand.grid(.mtry=c(3,5,8), .splitrule = "gini", .min.node.size = 5)
set.seed(200)
RF <- train(V1~., data=up_train, method="ranger", trControl = fitControl, tuneGrid = tunegrid)
RF
set.seed(200)
pred1 <- predict(RF, X_test_submission, type = 'raw')
pred1




```

```{r models}
## RF Ranger 90-99, 

fitControl <- trainControl(method = "repeatedcv", number = 10, verboseIter = TRUE, classProbs = TRUE)
rf_grid<-expand.grid(mtry = c(5, 8, 12), splitrule = c("gini", "extratrees"), min.node.size = c(3, 5, 7))
model_RF<-train(y ~ ., data = train_smote, method = "ranger", trControl = fitControl, num.trees=300, tuneGrid = rf_grid)

pred_RF <- predict(model_RF, newdata=X_test)

cm_RF_test <- confusionMatrix(factor(pred_RF), test$y)
cm_RF_train <- confusionMatrix(factor(predict(model_RF, newdata=X_train_smote)), train_smote$y)

balanced_accuracy_train <- cm_RF_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_RF_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)


## RF Ranger subm

rf_grid<-expand.grid(mtry = c(4, 6, 8), splitrule = c("gini", "extratrees"), min.node.size = c(5))
model_RF <- train(y ~ ., data = final_train_smote, method = "ranger", trControl = fitControl, num.trees=100, tuneGrid = rf_grid)

cm_pra_train <- confusionMatrix(factor(predict(model_RF, newdata=X_final_train_smote)), factor(final_train_smote$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

pred_RF <- predict(model_RF, newdata=X_test_submission)
```





```{r submit}
# this part is main code
subm_url = 'http://46.101.121.83'

u_name = "Error_Loading"
p_word = "UHAxWUfYKVZNQmgq"
submit_now = TRUE

username = u_name
password = p_word


token = get_token(username=u_name, password=p_word, url=subm_url)
## this part is where you need to provide your prediction method/function or set of R codes
## predictions=runif(2073) type double olduğu için çevirdim

pred <- pred2

pred_dummy <- mlr::createDummyFeatures(pred, pred, method="reference")

frame <- as.matrix(pred_dummy)

predictions <- frame

send_submission(predictions, token, url=subm_url, submit_now= submit_now)
```

# Related Literature
Summarize relevant literature if there is any
# Approach
Explain your approach to this problem.
# Results
Provide your results and discussion.
# Conclusions and Future Work
Summarize your findings and comments regarding your
approach. What are possible extensions to have a better approach?
# Code
The Github link for the codes is (HERE)[].





# PRA

# RF

