---
title: "Project_582"
author: "Error_Loading"
date: "1/26/2021"
output: 
  html_document:
      toc: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
          
---

1565 a
509 b

smote: k=5, perc.over = 100, perc.under=200
1018 a
1018 b
Aşağıdaki modeller bunu kullanıyor

PRA 78 test, 85 train, 0.8310786 subm
RF 78-99, 0.8378261 subm
RF2 78-99
DT 74-84
SGB 79 - 91, subm 0.8252871 besttune: 7-200-0.2
SGB 71-100, 9-300-0.3
SGB 76-100 , 9-200-0.3
SVM 0.8118033 tune etmeden subm, 0.8281884 tune ederek
SVM using Non-Linear Kernel subm 0.7992979


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, conflict=FALSE, warning=FALSE, message=FALSE, error = FALSE, comment = FALSE)
```

# Introduction
Problem description, summary of the proposed approach, descriptive
analysis of the given data.

```{r submission_functions_dont_touch}
require(jsonlite)
require(httr)
require(data.table)

get_token <- function(username, password, url_site){
    
    post_body = list(username=username,password=password)
    post_url_string = paste0(url_site,'/token/')
    result = POST(post_url_string, body = post_body)

    # error handling (wrong credentials)
    if(result$status_code==400){
        print('Check your credentials')
        return(0)
    }
    else if (result$status_code==201){
        output = content(result)
        token = output$key
    }

    return(token)
}

send_submission <- function(predictions, token, url_site, submit_now=F){
    
    format_check=check_format(predictions)
    if(!format_check){
        return(FALSE)
    }
    
    post_string="list("
    for(i in 1:length(predictions)){
        if(i<length(predictions)){
            post_string=sprintf("%s%s,",post_string,predictions[i])
        } else {
            post_string=sprintf("%s%s)",post_string,predictions[i])
        }
    }
    
    submission = eval(parse(text=post_string))
    json_body = jsonlite::toJSON(submission, auto_unbox = TRUE)
    submission=list(submission=json_body)
    print(submission)

    if(!submit_now){
        print("You did not submit.")
        return(FALSE)      
    }
    

    header = add_headers(c(Authorization=paste('Token',token,sep=' ')))
    post_url_string = paste0(url_site,'/submission/')
    result = POST(post_url_string, header, body=submission)
    
    if (result$status_code==201){
        print("Successfully submitted. Below you can see the details of your submission")
    } else {
        print("Could not submit. Please check the error message below, contact the assistant if needed.")
    }
    
    print(content(result))
    
}

check_format <- function(predictions){
    
    if(all(is.numeric(predictions)) & all(predictions<=1)){
        print("Format OK")
        return(TRUE)
    } else {
        print("Wrong format")
        return(FALSE)
    }
    
}
```


```{r libraries}
#importing the libraries
library(caret)
library(dplyr)
library(corrplot)
library(data.table)
library(glmnet)
library(rpart)
library(TunePareto)
library(randomForest)
library(tidyverse)
library(ggplot2)
library(pROC)
library(ROSE)
```

```{r dataset_manip}
train_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTrain.csv?token=ANPOH4IJOQLOLAD4XZY5ODTAFOXIC")
test_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTest.csv?token=ANPOH4JMDTUCP6TB4RWTZSTAFOXFY")

#skim(train_raw)

#no NA values, good
train_raw %>% summarise_all(~ sum(is.na(.))) 
test_raw %>% summarise_all(~ sum(is.na(.))) 

#to see the imbalance
train_raw %>% group_by(y) %>% summarize(count=n()) 
#ggplot(train_raw, aes(x=y )) + geom_bar(color="blue", fill=rgb(0.1,0.4,0.5,0.7) )

# train x50 ve x52 zero column, no variation, nothing to learn
# test x50 ve x52 zero değil ama öğrenmediğini predict edemez
# droplamak durumundayız
train <- train_raw %>% select(-x50, -x52, x57, x37)
X_test_submission <- test_raw %>% select(-x50, -x52, -x37, -x57, -y)

# make all colns double for smote
train_y <- mlr::createDummyFeatures(train$y, train$y,  method="reference")
trainx <- train %>% select(-y)
train <- cbind(as.data.table(trainx), as.data.table(train_y)) %>% rename(y=b)

set.seed(70)
smote <- smotefamily::SMOTE(X=train, target=train$y, K=1, dup_size = 2)

final_train_smote <- smote[["data"]] %>% select(-class)
final_train_smote %>% group_by(y) %>% summarize(count=n()) 

# cts olanlar ayrılıp scale edip cbind edilecek - X_test_submission ve train için, diğerleri factor yapılacak
colns <- colnames(final_train_smote)
cts_features <- c("x1", "x5", "x6", "x7", "x8", "x9", "x10", "x11", "x14", "x27", "x30", "x32", "x36", "x42")
categorical_features <- c("x2", "x3", "x4", "x12", "x13", "x15", "x16", "x17", "x18", "x19", "x20", "x21", "x22", "x23", "x24", "x25", "x26", "x28", "x29", "x31", "x33", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x47", "x48", "x49", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60")
categorical_features_y <- c("x2", "x3", "x4", "x12", "x13", "x15", "x16", "x17", "x18", "x19", "x20", "x21", "x22", "x23", "x24", "x25", "x26", "x28", "x29", "x31", "x33", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x47", "x48", "x49", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60", "y")

# scaling
train_cts_scaled <- final_train_smote %>% select(-y) %>% select(cts_features) %>% scale() %>% as.data.frame()

X_test_cts_scaled <-X_test_submission %>% select(cts_features) %>% scale() %>% as.data.frame()

# factorization for RF
train_categorical <- final_train_smote %>% select(categorical_features) %>% round(0)
train_categorical <- lapply(train_categorical, factor)
X_test_submission_categorical <- X_test_submission %>% select(categorical_features)
X_test_submission_categorical <- lapply(X_test_submission_categorical, factor)

train_categorical <- final_train_smote %>% select(categorical_features)

X_test_submission_categorical <- X_test_submission %>% select(categorical_features)

# scaled and factored
trainn <- cbind(as.data.table(train_cts_scaled), as.data.table(train_categorical), as.data.table(final_train_smote$y)) %>% rename(y=V1)
#levels(trainn$y) <- c("a", "b")
trainn$y <- as.factor(trainn$y)
final_train <- trainn
X_test_submission <- cbind(as.data.table(X_test_cts_scaled), as.data.table(X_test_submission_categorical))


#Correlation check
#corrplot(cor(train_cts_scaled, method = c("pearson")))
#corrplot(cor(X_test_cts_scaled, method = c("pearson")))

set.seed(1)
train_inds <- createDataPartition(y = 1:nrow(trainn), p = 0.8, list = F)
test <- trainn[-train_inds, ]
train <- trainn[train_inds, ]

train <- train
X_train <- train %>% select(-y)
y_train <- train %>% select(y)
X_test <- test %>% select(-y)
y_test <- test %>% select(y)



# aşağıdaki kodlar kolay çalışsın diye;
final_train_smote <- final_train
X_final_train_smote <- final_train_smote %>% select(-y)
y_final_train_smote <- final_train_smote %>% select(y)

train_smote <- train
X_train_smote <- X_train
y_train_smote <- y_train
```




```{r gbm}
## SGB
## 79 -91, params 7, 200, 0.2,10, subm 0.8252871
## 89-97, params 7, 200, 0.1, 10, train96-subm83
## 89-1, params 7, 500, 0.1, 10, train99-subm83
## 89-93, params 7, 1000, 0.01, 10 train93-subm8416
## 88-89, params 7, 3000, 0.001, 10 train89-subm82
## 86-87, params 9, 1000, 0.001, 5
## 88-89, params 9, 2000, 0.001, 5
## 86-87, params 5, 2000, 0.001, 5


## 71-100, 9-300-0.3
## 76-100 , 9-200-0.3
set.seed(1)
n_folds <- 10
fitControl <- trainControl(method = "repeatedcv", number = n_folds, verboseIter = FALSE, allowParallel = FALSE)  

gbmGrid_forever <-  expand.grid(interaction.depth = c(1, 5, 7), n.trees = c(50,100,200), shrinkage = c(0.05, 0.1, 0.2), n.minobsinnode = c(10))

gbmGrid <-  expand.grid(interaction.depth = c(7), n.trees = c(2000), shrinkage = c(0.001), n.minobsinnode = c(10))

#train_smote <- train_smote %>% select(-x37)
#distribution="bernoulli"
model_sgb <- train(y ~ ., data = data.frame(train_smote), method = "gbm", trControl = fitControl, tuneGrid = gbmGrid, verbose=F)

pred_sgb <- predict(model_sgb, newdata=X_test) %>% as.matrix()

cm_sgb_test <- confusionMatrix(factor(pred_sgb), factor(y_test$y))
cm_sgb_train <- confusionMatrix(factor(predict(model_sgb, newdata=X_train_smote)), factor(y_train_smote$y))

balanced_accuracy_train <- cm_sgb_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_sgb_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)



#### subm

#final_train_smote <- final_train_smote %>% select(-x37)
model_sgb <- train(y ~ ., data = data.frame(final_train_smote), method = "gbm", trControl = fitControl, tuneGrid = gbmGrid, verbose=F)


cm_sgb_train <- confusionMatrix(factor(predict(model_sgb, newdata=X_final_train_smote)), factor(y_final_train_smote$y))
print(cm_sgb_train[["byClass"]][["Balanced Accuracy"]])

pred_sgb <- predict(model_sgb, newdata=X_test_submission) %>% as.matrix()


```


```{r rf}

## RF 90-98 
m<-c(8, 10, 12, 15)
#for balanced folds: stratified =TRUE
# ntree is J=500 given in hw
J<-1000
# the minimal number of observations per tree leaf is nodesize 5 given in hw
min_size_of_terminal_nodes<-c(3, 5, 7)
n_folds<-5
fitControl<-trainControl(method = "repeatedcv", number = n_folds, repeats = 1, classProbs = TRUE, search="random", savePred=TRUE)   
rf_grid<-expand.grid(mtry = m, nodesize=min_size_of_terminal_nodes)

model_RF <- train(y ~ ., data = train_smote, method = "rf", metric="ROC", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid)

pred_RF <- predict(model_RF, newdata=X_test)

cm_RF_test <- confusionMatrix(factor(pred_RF), factor(test$y))
cm_RF_train <- confusionMatrix(factor(predict(model_RF, newdata=X_train_smote)), factor(train_smote$y))

balanced_accuracy_test <- cm_RF_test[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_train <- cm_RF_train[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_test)
print(balanced_accuracy_train)

######  subm

model_RF <- train(y ~ ., data = final_train_smote, method = "rf", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid)

cm_pra_train <- confusionMatrix(factor(predict(model_RF, newdata=X_final_train_smote)), factor(final_train_smote$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

pred_RF <- predict(model_RF, newdata=X_test_submission)


```


```{r pra}




```




```{r submit}
# this part is main code
subm_url = 'http://46.101.121.83'

u_name = "Error_Loading"
p_word = "UHAxWUfYKVZNQmgq"
submit_now = TRUE

username = u_name
password = p_word


token = get_token(username=u_name, password=p_word, url=subm_url)
## this part is where you need to provide your prediction method/function or set of R codes
## predictions=runif(2073) type double olduğu için çevirdim

pred <- pred_sgb

pred_dummy <- mlr::createDummyFeatures(pred, pred, method="reference")

frame <- as.matrix(pred_dummy)

predictions <- frame

send_submission(predictions, token, url=subm_url, submit_now= submit_now)
```

# Related Literature
Summarize relevant literature if there is any
# Approach
Explain your approach to this problem.
# Results
Provide your results and discussion.
# Conclusions and Future Work
Summarize your findings and comments regarding your
approach. What are possible extensions to have a better approach?
# Code
The Github link for the codes is (HERE)[].





# PRA

# RF

