---
title: "Project_582"
author: "Error_Loading"
date: "1/26/2021"
output: 
  html_document:
      toc: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
          
---

train_raw %>% group_by(y) %>% summarize(count=n()) 
1565 a
509 b

DMwR::SMOTE: k=5, perc.over = 200, perc.under=200
2036 a
1527 b
Aşağıdaki modeller bunu kullanıyor
smotefamily::SMOTE

PRA test 84, train 81 seed70
RF 90-98, subm0.841
RF2 90test-99train 0.84subm
DT 84-84
SGB 88 -100 no tune, 89-90 tune with gbmGrid_forever, 82 subm
82-81 "svmLinear" 
88-95 "svmRadial" subm76
NN 85-93, subm 81.2



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, conflict=FALSE, warning=FALSE, message=FALSE, error = FALSE, comment = FALSE)
```

# Introduction
Problem description, summary of the proposed approach, descriptive
analysis of the given data.

```{r submission_functions_dont_touch}
require(jsonlite)
require(httr)
require(data.table)

get_token <- function(username, password, url_site){
    
    post_body = list(username=username,password=password)
    post_url_string = paste0(url_site,'/token/')
    result = POST(post_url_string, body = post_body)

    # error handling (wrong credentials)
    if(result$status_code==400){
        print('Check your credentials')
        return(0)
    }
    else if (result$status_code==201){
        output = content(result)
        token = output$key
    }

    return(token)
}

send_submission <- function(predictions, token, url_site, submit_now=F){
    
    format_check=check_format(predictions)
    if(!format_check){
        return(FALSE)
    }
    
    post_string="list("
    for(i in 1:length(predictions)){
        if(i<length(predictions)){
            post_string=sprintf("%s%s,",post_string,predictions[i])
        } else {
            post_string=sprintf("%s%s)",post_string,predictions[i])
        }
    }
    
    submission = eval(parse(text=post_string))
    json_body = jsonlite::toJSON(submission, auto_unbox = TRUE)
    submission=list(submission=json_body)
    print(submission)

    if(!submit_now){
        print("You did not submit.")
        return(FALSE)      
    }
    

    header = add_headers(c(Authorization=paste('Token',token,sep=' ')))
    post_url_string = paste0(url_site,'/submission/')
    result = POST(post_url_string, header, body=submission)
    
    if (result$status_code==201){
        print("Successfully submitted. Below you can see the details of your submission")
    } else {
        print("Could not submit. Please check the error message below, contact the assistant if needed.")
    }
    
    print(content(result))
    
}

check_format <- function(predictions){
    
    if(all(is.numeric(predictions)) & all(predictions<=1)){
        print("Format OK")
        return(TRUE)
    } else {
        print("Wrong format")
        return(FALSE)
    }
    
}
```


```{r libraries}
#importing the libraries
library(caret)
library(dplyr)
library(corrplot)
library(data.table)
library(glmnet)
library(rpart)
library(TunePareto)
library(randomForest)
library(tidyverse)
library(ggplot2)
library(pROC)
library(ROSE)
library(nnet)
library(skimr)
```

```{r dataset_manip}
train_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTrain.csv?token=ANPOH4IJOQLOLAD4XZY5ODTAFOXIC")
test_raw <- read.csv("https://raw.githubusercontent.com/ilaydacelenk/Error_Loading/master/IE582_Fall20_ProjectTest.csv?token=ANPOH4JMDTUCP6TB4RWTZSTAFOXFY")

skim(train_raw)

#no NA values, good
train_raw %>% summarise_all(~ sum(is.na(.))) 
test_raw %>% summarise_all(~ sum(is.na(.))) 

#to see the imbalance
train_raw %>% group_by(y) %>% summarize(count=n()) 
#ggplot(train_raw, aes(x=y )) + geom_bar(color="blue", fill=rgb(0.1,0.4,0.5,0.7) )

# train x50 ve x52 zero column, no variation, nothing to learn
# test x50 ve x52 zero değil ama öğrenmediğini predict edemez
# droplamak durumundayız
train <- train_raw %>% select(-x50, -x52, x57, x37)
X_test_submission <- test_raw %>% select(-x50, -x52, -x37, -x57, -y)

# make all colns double for smote
train_y <- mlr::createDummyFeatures(train$y, train$y,  method="reference")
trainx <- train %>% select(-y)
train <- cbind(as.data.table(trainx), as.data.table(train_y)) %>% rename(y=b)

set.seed(70)
smote <- smotefamily::SMOTE(X=train, target=train$y, K=1, dup_size = 2)

final_train_smote <- smote[["data"]] %>% select(-class)
final_train_smote %>% group_by(y) %>% summarize(count=n()) 

# cts olanlar ayrılıp scale edip cbind edilecek - X_test_submission ve train için, diğerleri factor yapılacak
colns <- colnames(final_train_smote)
cts_features <- c("x1", "x5", "x6", "x7", "x8", "x9", "x10", "x11", "x14", "x27", "x30", "x32", "x36", "x42")
categorical_features <- c("x2", "x3", "x4", "x12", "x13", "x15", "x16", "x17", "x18", "x19", "x20", "x21", "x22", "x23", "x24", "x25", "x26", "x28", "x29", "x31", "x33", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x47", "x48", "x49", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60")
categorical_features_y <- c("x2", "x3", "x4", "x12", "x13", "x15", "x16", "x17", "x18", "x19", "x20", "x21", "x22", "x23", "x24", "x25", "x26", "x28", "x29", "x31", "x33", "x34", "x35", "x38", "x39", "x40", "x41", "x43", "x44", "x45", "x46", "x47", "x48", "x49", "x51", "x53", "x54", "x55", "x56", "x58", "x59", "x60", "y")

# scaling
train_cts_scaled <- final_train_smote %>% select(-y) %>% select(cts_features) %>% scale() %>% as.data.frame()

X_test_cts_scaled <-X_test_submission %>% select(cts_features) %>% scale() %>% as.data.frame()

# factorization
train_categorical <- final_train_smote %>% select(categorical_features)
train_categorical <- lapply(train_categorical, factor)
X_test_submission_categorical <- X_test_submission %>% select(categorical_features)
X_test_submission_categorical <- lapply(X_test_submission_categorical, factor)

train_categorical <- final_train_smote %>% select(categorical_features)

X_test_submission_categorical <- X_test_submission %>% select(categorical_features)

# scaled and factored
trainn <- cbind(as.data.table(train_cts_scaled), as.data.table(train_categorical), as.data.table(final_train_smote$y)) %>% rename(y=V1)
#levels(trainn$y) <- c("a", "b")
trainn$y <- as.factor(trainn$y)
final_train <- trainn
X_test_submission <- cbind(as.data.table(X_test_cts_scaled), as.data.table(X_test_submission_categorical))


#Correlation check
#corrplot(cor(train_cts_scaled, method = c("pearson")))
#corrplot(cor(X_test_cts_scaled, method = c("pearson")))

set.seed(1)
train_inds <- createDataPartition(y = 1:nrow(trainn), p = 0.8, list = F)
test <- trainn[-train_inds, ]
train <- trainn[train_inds, ]

train <- train
X_train <- train %>% select(-y)
y_train <- train %>% select(y)
X_test <- test %>% select(-y)
y_test <- test %>% select(y)



# aşağıdaki kodlar kolay çalışsın diye;
final_train_smote <- final_train
X_final_train_smote <- final_train_smote %>% select(-y)
y_final_train_smote <- final_train_smote %>% select(y)

train_smote <- train
X_train_smote <- X_train
y_train_smote <- y_train
```

```{r models}
## PRA test 84, train 81 seed70
## RF 90-98, subm0.841
## RF2 90test-99train 0.84subm
## DT 84-84
## SGB 88 -100 no tune, 89-90 tune with gbmGrid_forever, 82 subm
# 82-81 "svmLinear" 
# 88-95 "svmRadial" subm76
## NN 85-93, subm 81.2



## RF 90-98 
set.seed(50)
m=c(8, 10, 12)
#for balanced folds: stratified =TRUE
# ntree is J=500 given in hw
J=500 
# the minimal number of observations per tree leaf is nodesize 5 given in hw
min_size_of_terminal_nodes=5
n_folds=5
fitControl<-trainControl(method = "repeatedcv", number = n_folds, repeats = 1, classProbs = TRUE, search="random", savePred=TRUE)   
rf_grid<-expand.grid(mtry = m)

model_RF <- train(y ~ ., data = train_smote, method = "rf", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid)

pred_RF <- predict(model_RF, newdata=X_test)

cm_RF_test <- confusionMatrix(factor(pred_RF), factor(test$y))
cm_RF_train <- confusionMatrix(factor(predict(model_RF, newdata=X_train_smote)), factor(train_smote$y))

balanced_accuracy_test <- cm_RF_test[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_train <- cm_RF_train[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_test)
print(balanced_accuracy_train)


######  0.841

model_RF <- train(y ~ ., data = final_train_smote, method = "rf", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid)

cm_pra_train <- confusionMatrix(factor(predict(model_RF, newdata=X_final_train_smote)), factor(final_train_smote$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

pred_RF <- predict(model_RF, newdata=X_test_submission, type = 'prob')


## RF2 90test-99train
m=c(12, 15, 20)
#for balanced folds: stratified =TRUE
# ntree is J=500 given in hw
J=500 
# the minimal number of observations per tree leaf is nodesize 5 given in hw
min_size_of_terminal_nodes=5
n_folds=10
fitControl=trainControl(method = "repeatedcv", number = n_folds, repeats = 1, classProbs = FALSE, search="random", savePred=TRUE)   
rf_grid<-expand.grid(mtry = m)

model_RF <- train(y ~ ., data = train_smote, method = "rf", trControl = fitControl, ntree=J, nodesize=min_size_of_terminal_nodes, tuneGrid = rf_grid)

pred_RF <- predict(model_RF, newdata=X_test)

cm_RF_test <- confusionMatrix(factor(pred_RF), test$y)
cm_RF_train <- confusionMatrix(factor(predict(model_RF, newdata=X_train_smote)), train_smote$y)

balanced_accuracy_train <- cm_RF_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_RF_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)

######  0.84

model_RF <- train(y ~ ., data = final_train_smote, method = "rf", trControl = fitControl, ntree=J, nodesize = min_size_of_terminal_nodes, tuneGrid = rf_grid)

cm_pra_train <- confusionMatrix(factor(predict(model_RF, newdata=X_final_train_smote)), factor(final_train_smote$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

pred_RF <- predict(model_RF, newdata=X_test_submission)




## RF Ranger 90-99, 

fitControl <- trainControl(method = "repeatedcv", number = 10, verboseIter = TRUE, classProbs = TRUE)
rf_grid<-expand.grid(mtry = c(3, 5, 7, 11, 15), splitrule = c("gini", "extratrees"), min.node.size = c(3, 5, 7))
model_RF<-train(y ~ ., data = train_smote, method = "ranger", trControl = fitControl, num.trees=250, tuneGrid = rf_grid)

pred_RF <- predict(model_RF, newdata=X_test)

cm_RF_test <- confusionMatrix(factor(pred_RF), test$y)
cm_RF_train <- confusionMatrix(factor(predict(model_RF, newdata=X_train_smote)), train_smote$y)

balanced_accuracy_train <- cm_RF_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_RF_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)


## RF Ranger subm

rf_grid<-expand.grid(mtry = c(4, 6, 8), splitrule = c("gini", "extratrees"), min.node.size = c(5))
model_RF <- train(y ~ ., data = final_train_smote, method = "ranger", trControl = fitControl, num.trees=100, tuneGrid = rf_grid)

cm_pra_train <- confusionMatrix(factor(predict(model_RF, newdata=X_final_train_smote)), factor(final_train_smote$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

pred_RF <- predict(model_RF, newdata=X_test_submission)



## DT 91-84

set.seed(280)
complexity=c(0.001, 0.01,0.03,0.05)
min_number_of_observations=c(5, 7, 10, 15, 25)
cv_summary=data.table()

#for balanced folds: stratified =TRUE
index <- generateCVRuns(train_smote$y, ntimes=3, nfold=10, stratified =TRUE)
acc <- 0
best_complexity <- 0
best_min_number_of_observations <- 0
for(i in 1:10){
  for(c in complexity){
    for(m in min_number_of_observations){
      test_index <- index$`Run  1`[i]
      train_cv <- train_smote[-test_index[[1]],]
      test_cv <- train_smote[test_index[[1]],]
      fitControl <- rpart.control(cp = c, minbucket = m)  
      model_DT=rpart(y~., train_smote, control=fitControl)
      pred <- predict(model_DT, test_cv, type="class")
      cm <- confusionMatrix(pred, factor(test_cv$y))
      acc_temp <- cm$overall[1:1]
      cv_summary <- rbind(cv_summary,data.table(Fold=i, Complexity=c, Min_Observations_per_Leaf=m, Accuracy=acc_temp))

      if(acc_temp>acc){
        acc<-acc_temp
        best_complexity <- c
        best_min_number_of_observations <- m
      }
    }
  }
}

cv_summary <- cv_summary %>% group_by(Complexity, Min_Observations_per_Leaf) %>% summarise(mean_accuracy = mean(Accuracy))
print(cv_summary)

fitControl <- rpart.control(cp = best_complexity, minbucket = best_min_number_of_observations)
model_DT <- rpart(y~., train_smote, control=fitControl)
pred_DT <- predict(model_DT, X_test, type="class")

cm_DT_test <- confusionMatrix(factor(pred_DT), factor(test$y))
cm_DT_train <- confusionMatrix(factor(predict(model_DT, X_train_smote, type="class")), factor(y_train_smote$y))

balanced_accuracy_train <- cm_DT_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_DT_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)


## DT subm
set.seed(280)
complexity=c(0.001, 0.01,0.03,0.05)
min_number_of_observations=c(5, 7, 10,15,25)
cv_summary=data.table()

#for balanced folds: stratified =TRUE
index <- generateCVRuns(final_train_smote$y, ntimes=1, nfold=10, stratified =TRUE)
acc <- 0
best_complexity <- 0
best_min_number_of_observations <- 0
for(i in 1:10){
  for(c in complexity){
    for(m in min_number_of_observations){
      test_index <- index$`Run  1`[i]
      train_cv <- final_train_smote[-test_index[[1]],]
      test_cv <- final_train_smote[test_index[[1]],]
      fitControl <- rpart.control(cp = c, minbucket = m)  
      model_DT<-rpart(y~., final_train_smote, control=fitControl)
      pred <- predict(model_DT, test_cv, type="class")
      cm <- confusionMatrix(pred, factor(test_cv$y))
      acc_temp <- cm$overall[1:1]
      cv_summary <- rbind(cv_summary,data.table(Fold=i, Complexity=c, Min_Observations_per_Leaf=m, Accuracy=acc_temp))

      if(acc_temp>acc){
        acc<-acc_temp
        best_complexity <- c
        best_min_number_of_observations <- m
      }
    }
  }
}

cv_summary <- cv_summary %>% group_by(Complexity, Min_Observations_per_Leaf) %>% summarise(mean_accuracy = mean(Accuracy))
print(cv_summary)

fitControl <- rpart.control(cp = best_complexity, minbucket = best_min_number_of_observations)
model_DT <- rpart(y~., final_train_smote, control=fitControl)
pred_DT <- predict(model_DT, X_final_train_smote, type="class")

cm_DT_train <- confusionMatrix(factor(pred_DT), factor(final_train_smote$y))

balanced_accuracy_train <- cm_DT_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)


## SGB 88 -100 no tune, 89-90 tune with gbmGrid_forever, 82 subm

set.seed(50)
n_folds <- 10
fitControl <- trainControl(method = "cv", number = n_folds)  

gbmGrid_forever <-  expand.grid(interaction.depth = c(1, 3, 5), n.trees = c(50,100,150, 200), shrinkage = c(0.05, 0.1, 0.2), n.minobsinnode = c(10, 20))

gbmGrid <-  expand.grid(interaction.depth = c(9), n.trees = c(200), shrinkage = c(0.3), n.minobsinnode = c(10))

model_sgb<-train(y ~ ., data = data.frame(train_smote), method = "gbm", trControl = fitControl, tuneGrid = gbmGrid, verbose=F)

pred_sgb <- predict(model_sgb, newdata=X_test) %>% as.matrix()

cm_sgb_test <- confusionMatrix(factor(pred_sgb), factor(y_test$y))
cm_sgb_train <- confusionMatrix(factor(predict(model_sgb, newdata=X_train_smote)), factor(y_train_smote$y))

balanced_accuracy_train <- cm_sgb_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_sgb_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)


#### 82 subm

model_sgb <- train(y ~ ., data = data.frame(final_train_smote), method = "gbm", trControl = fitControl, tuneGrid = gbmGrid_forever, verbose=F)

cm_pra_train <- confusionMatrix(factor(predict(model_sgb, newdata=X_final_train_smote)), factor(final_train_smote$y))
balanced_accuracy_train <- cm_pra_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)


pred_sgb <- predict(model_sgb, newdata=X_test_submission) %>% as.matrix()
# n.trees = 200, interaction.depth = 7, shrinkage = 0.2 and n.minobsinnode = 10



## SVM 
# 82-81 "svmLinear" 
set.seed(50)
train_control <- trainControl(method="repeatedcv", number=10, repeats=3)
svm1 <- train(y ~., data = data.frame(train_smote), method = "svmLinear", trControl = train_control,  preProcess = c("center","scale"), tuneGrid = expand.grid(C = seq(0.01, 2, length = 20)))


pred_svm <- predict(svm1, newdata=X_test) %>% as.matrix()

cm_svm_test <- confusionMatrix(factor(pred_svm), test$y)
cm_svm_train <- confusionMatrix(factor(predict(svm1, newx=data.matrix(X_train_smote))), train_smote$y)

balanced_accuracy_train <- cm_svm_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_svm_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)

#### model 

set.seed(50)
grid <- expand.grid(C = seq(0.01, 2, length = 20))
train_control <- trainControl(method="repeatedcv", number=10, repeats=3)
svm2 <- train(y ~., data = data.frame(final_train_smote), method = "svmLinear", trControl = train_control,  preProcess = c("center","scale"),tuneGrid = expand.grid(C = seq(0.01, 2, length = 20)))

pred_svm <- predict(svm2, newdata=X_test_submission) %>% as.matrix()

cm_svm_train <- confusionMatrix(factor(predict(svm2, newx=data.matrix(X_final_train_smote))), final_train_smote$y)

balanced_accuracy_train <- cm_svm_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

## SVM using Non-Linear Kernel 
# 88-95 "svmRadial" subm76

set.seed(50)
train_control <- trainControl(method="repeatedcv", number=10, repeats=3)
svm3 <- train(y ~., data = train_smote, method = "svmRadial", trControl = train_control, preProcess = c("center","scale"), tuneLength = 10)

pred_svm <- predict(svm3, newdata=X_test) %>% as.matrix()

cm_svm_test <- confusionMatrix(factor(pred_svm), test$y)
cm_svm_train <- confusionMatrix(factor(predict(svm3, newx=data.matrix(X_train_smote))), train_smote$y)

balanced_accuracy_train <- cm_svm_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_svm_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)


## model 

svm3 <- train(y ~., data = final_train_smote, method = "svmRadial", trControl = train_control, preProcess = c("center","scale"), tuneLength = 10)

pred_svm <- predict(svm3, newdata=X_test_submission) %>% as.matrix()
cm_svm_train <- confusionMatrix(factor(predict(svm3, newx=data.matrix(X_final_train_smote))), final_train_smote$y)
balanced_accuracy_train <- cm_svm_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)


## NN 85-93 , subm 81.2

set.seed(50)
grid <- expand.grid(.decay=c(0.7, 0.5, 0.1), .size=c(7, 8, 9))
train_control <- trainControl(method="repeatedcv", number=10, repeats=3)
train_smote <- train_smote %>% select(-x37)
X_train_smote <- X_train_smote %>% select(-x37)
nn_model <- train(x=X_train_smote, y=train_smote$y, method = "nnet", trControl = train_control, preProc = c("center", "scale"), tuneGrid=grid, maxit=100, trace=FALSE, linout = FALSE)

pred_nn <- predict(nn_model, newdata=X_test) %>% as.matrix()

cm_nn_test <- confusionMatrix(factor(pred_nn), test$y)
cm_nn_train <- confusionMatrix(factor(predict(nn_model, newx=data.matrix(X_train_smote))), train_smote$y)

balanced_accuracy_train <- cm_nn_train[["byClass"]][["Balanced Accuracy"]]
balanced_accuracy_test <- cm_nn_test[["byClass"]][["Balanced Accuracy"]]

print(balanced_accuracy_train)
print(balanced_accuracy_test)

#### model 0.812

set.seed(50)
grid <- expand.grid(.decay=c(0.7, 0.5, 0.1), .size=c(7, 9, 11))
train_control <- trainControl(method="repeatedcv", number=10, repeats=3)
train_smote <- train_smote %>% select(-x37)
X_train_smote <- X_train_smote %>% select(-x37)
final_train_smote2 <- final_train_smote %>% select(-x37)
nn_model <- train(y ~., data = final_train_smote2, method = "nnet", trControl = train_control, preProc = c("center", "scale"), tuneGrid=grid, maxit=100, trace=FALSE, linout = FALSE)

pred_nn <- predict(nn_model, newdata=X_test_submission) %>% as.matrix()

cm_nn_train <- confusionMatrix(factor(predict(nn_model, newx=data.matrix(X_final_train_smote))), final_train_smote$y)

balanced_accuracy_train <- cm_nn_train[["byClass"]][["Balanced Accuracy"]]
print(balanced_accuracy_train)

```





```{r submit}
# this part is main code
subm_url = 'http://46.101.121.83'

u_name = "Error_Loading"
p_word = "UHAxWUfYKVZNQmgq"
submit_now = TRUE

username = u_name
password = p_word


token = get_token(username=u_name, password=p_word, url=subm_url)
## this part is where you need to provide your prediction method/function or set of R codes
## predictions=runif(2073) type double olduğu için çevirdim

pred <- pred_DT

pred_dummy <- mlr::createDummyFeatures(pred, pred, method="reference")

frame <- as.matrix(pred_dummy)

predictions <- frame

send_submission(predictions, token, url=subm_url, submit_now= submit_now)
```

# Related Literature
Summarize relevant literature if there is any
# Approach
Explain your approach to this problem.
# Results
Provide your results and discussion.
# Conclusions and Future Work
Summarize your findings and comments regarding your
approach. What are possible extensions to have a better approach?
# Code
The Github link for the codes is (HERE)[].





# PRA

# RF

